Lexicalized Domain Representations for Neural Machine Translation

### 2019-05-21 2019/emnlp/sparse.tex
sec3

To check the validity of this hypothesis, we performed the following analysis of embeddings learned with the multi-domain Transformer system for en:fr. For each unit\footnote{In this study, we work with BPE units, not words, meaning that in many cases we observe the variation of use of word parts. As we work with a large inventory, many of these units correspond to actual words, and we focus on these in our comments. We also restrict our analysis to words that occur at least 30 times in each domain, to ensure that each domain-specific region is updated during training.} in our English dictionary, we compute the $k$ nearest neighbours for each domain $i \in [1\dots{}d]$, where the distance between unit $u$ and $v$ for domain $i$ is the cosine distance in the corresponding embedding space, ie.\ assuming that the actual embedding of $v$ for domain $d$ is $e(v,i) = M_ge_g(u) + M_de_i(v)$ (cf.\ equation~\eqref{}).\fyTodo{Equation}. This process yields $d$ lists of $k$ nearest neighbours. The size of their intersection should then be a sign of a variation of use across domains; conversely, an identical set of neighbours across domains should reflect the stability of word use. Table~\ref{tab:embeddings} list the 10 units with the smaller (respectively larger) intersection (we use $k=10$ and $d=3$).

>>>>

To check the validity of this hypothesis, we performed the following analysis of embeddings learned with the multi-domain Transformer system for English:French. For each unit\footnote{In this study, we work with BPE units, not words, meaning that in many cases we observe the variation of use of word parts. As we work with a large inventory, many of these units correspond to actual words, and we focus on these in our comments. We also restrict our analysis to words that occur at least 30 times in each domain, to ensure that each domain-specific region is updated during training.} in our English dictionary, we compute the $k$ nearest neighbours for each domain $i \in [1\dots{}d]$, where the distance between unit $u$ and $v$ for domain $i$ is the cosine distance in the corresponding embedding space, ie.\ assuming that the actual embedding of $v$ for domain $d$ is $e(v,i) = M_ge_g(u) + M_de_i(v)$ (cf.\ equation~\eqref{}).\fyTodo{Equation}. This process yields $d$ lists of $k$ nearest neighbours. The size of their intersection should then be a sign of a variation of use across domains; conversely, an identical set of neighbours across domains should reflect the stability of word use. Table~\ref{tab:embeddings} list the 10 units with the smaller (respectively larger) intersection (we use $k=10$ and $d=3$).
